---
title: "Lab 8"
author: ""
output:
  pdf_document: default
---

```{r, include = F}
library(dplyr)
library(readr)
library(knitr)
set.seed(10302019)
```


## Lab Overview

For this lab we will look at the impact of weather on bike rentals using the (infamous) Capital Bikeshare dataset. The data set contains total number of daily bike rentals across a two year period. For each date there are also a set of weather variables. We will restrict our inference to the (astronomical) summer season with a goal of predicting total bike rentals across the 188 days.

```{r, message = F}
bike_rentals <- read_csv('http://math.montana.edu/ahoegh/teaching/stat446/daily_bike.csv')
bike_summer <- bike_rentals %>% filter(season == 3) %>% select(cnt, dteday, yr, mnth, temp, hum, windspeed, workingday, weekday, weathersit)
bike_summer
```


### Data Dictionary


dteday: Date
yr: Year (0: 2011, 1:2012)
mnth: Month (1 to 12)
holiday: weather day is holiday or not (extracted from Holiday Schedule)
temp: Normalized temperature in Celsius. The values are derived via (t-t_min)/(t_max-t_min),
hum: Normalized humidity. The values are divided to 100 (max)
windspeed: Normalized wind speed. The values are divided to 67 (max)
weekday: Day of the week
workingday: If day is neither weekend nor holiday is 1, otherwise is 0.
weathersit: (extracted from Freemeteo)
1: Clear, Few clouds, Partly cloudy, Partly cloudy
2: Mist + Cloudy, Mist + Broken clouds, Mist + Few clouds, Mist
3: Light Snow, Light Rain + Thunderstorm + Scattered clouds, Light Rain + Scattered clouds
4: Heavy Rain + Ice Pallets + Thunderstorm + Mist, Snow + Fog
cnt: count of total rental bikes including both casual and registered



##### Acknowledgements:

Hadi Fanaee-T Laboratory of Artificial Intelligence and Decision Support (LIAAD), University of Porto INESC Porto, Campus da FEUP Rua Dr. Roberto Frias, 378 4200 - 465 Porto, Portugal

Original Source: http://capitalbikeshare.com/system-data

Weather Information: http://www.freemeteo.com

Holiday Schedule: http://dchr.dc.gov/page/holiday-schedule



#### 1. (20 points)
Propose and carryout a sampling scheme with the goal of estimating the total number of bikes rented for the 188 days. The lab should consist of a short writeup that parallels the project. The only requirements are to have a point estimate and associated confidence interval for the result. Note you are welcome to use any sampling / estimation approaches, but make sure to defend those choices. You can take a total of 40 samples in whatever sampling scheme you choose.


##### Introduction
Brief overview of the question of interest.

##### Sampling Scheme
Detail the sampling and estimation approaches.

##### Results
Discuss the results of your sampling and estimation.

##### Discussion
Summary of your results, assume this is written for employees at Capital Bikeshare.



